Pillar 1 - Sequential Pattern Mining

### 2019-02-12 Pillar 1 - Sequential Pattern Mining.Rmd
simplify code summary statistics

# For convenience
provide_statistics <- function(data){

  data %>%
    summarise(
      Min       = min(Grade),
      Max       = max(Grade), 
      Mean      = mean(Grade), 
      Median    = median(Grade), 
      SD        = sd(Grade),
      `Failure Rate` = mean(Fail),
      `Failure Count`    = sum(Fail),
      Count     = n()
      ) %>%
    mutate_at(
      vars(Mean, SD, `Failure Rate`),
      round,
      digits = 2
    )

@@

# Student level
statistics_student <- d_transcript %>%
  group_by(`Student ID`) %>%
  provide_statistics()

# Course level
statistics_course <- d_transcript %>%
  inner_join(d_course, by = c("Course ID")) %>%
  group_by(`Course ID`) %>%
  provide_statistics()

# Cluster level
statistics_cluster <- d_transcript %>%
  inner_join(d_course, by = "Course ID") %>%
  filter(!is.na(Cluster)) %>%
  group_by(Cluster) %>%
  provide_statistics()

# Type level
statistics_type <- d_transcript %>%
  inner_join(d_course, by = "Course ID") %>%
  filter(!is.na(Type)) %>%
  group_by(Type) %>%
  provide_statistics()

# Concentration evel
statistics_concentration <- d_transcript %>%
  inner_join(d_course, by = "Course ID") %>%
  gather(X, Concentration, Concentration, `Concentration (additional)`, na.rm = TRUE) %>%
  group_by(Concentration) %>%
  provide_statistics()

# Year level
statistics_year <- d_transcript %>%
  group_by(Year_numerical) %>%
  provide_statistics()

# Level level
statistics_level <- d_transcript %>%
  # TODO: filter for student who completed their studies
  inner_join(d_course, by = c("Course ID")) %>%
  filter(!is.na(Level)) %>%
  group_by(Level) %>%
  provide_statistics()

#
# output
save(statistics_student, statistics_course, statistics_cluster,
     statistics_concentration, statistics_year, statistics_level, file = "Output/Transcript Statistics.RDATA")

#rm(provide_statistics, statistics_student, statistics_course, statistics_cluster,
#     statistics_concentration, statistics_year, statistics_level)
```

>>>>

#
# function providing statistics
provide_statistics <- function(data, var){

  data %>%
    filter(
      !is.na(!!enquo(var))
      ) %>%
    group_by(
      !!enquo(var)
      ) %>%
    summarise(
      Min             = min(Grade),
      Max             = max(Grade), 
      Mean            = mean(Grade), 
      Median          = median(Grade), 
      SD              = sd(Grade),
      `Failure Rate`  = mean(Fail),
      `Failure Count` = sum(Fail),
      Count           = n()
      ) %>%
    mutate_at(
      vars(Mean, SD, `Failure Rate`),
      round,
      digits = 2
    )

@@

#
# Generating Statistics
statistics <- list()

# Student level
statistics$student <- d_transcript %>%
  provide_statistics(`Student ID`)

# Course level
statistics$course <- d_transcript %>%
  inner_join(
    d_course,
    by = c("Course ID")
    ) %>%
  provide_statistics(`Course ID`)

# Cluster level
statistics_cluster <- d_transcript %>%
  inner_join(
    d_course, 
    by = "Course ID"
    ) %>%
  provide_statistics(Cluster)

# Type level
statistics_type <- d_transcript %>%
  inner_join(
    d_course, by = "Course ID"
    ) %>%
  provide_statistics(Type)

# Concentration evel
statistics_concentration <- d_transcript %>%
  inner_join(d_course, by = "Course ID") %>%
  gather(X, Concentration, Concentration, `Concentration (additional)`, na.rm = TRUE) %>%
  provide_statistics(Concentration)

# Year level
statistics_year <- d_transcript %>%
  provide_statistics(Year_numerical)

# Level level
statistics_level <- d_transcript %>%
  # TODO: filter for student who completed their studies
  inner_join(d_course, by = c("Course ID")) %>%
  provide_statistics(Level)

#
# output
save(
  statistics,
  file = "Output/Transcript Statistics.RDATA"
  )

rm(statistics)
```
